---
title: "206 A5 Q4"
author: "Barbara Rose Hoover"
date: "12/4/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r loading packages}
library(tidyverse)
library(stargazer)
library(MASS)
```


```{r preparing data}
faculty <- read_csv("Faculty.csv")

faculty <- rename(faculty, discipline = `Discipline (A = Theoretical, B = Applied)`, rank = `Faculty Rank`, yearsphd = `Years Since PhD`, yearsfac = `Years Faculty Service`, sex = Sex, salary = `Salary ($)`)
```


Linear Model 
```{r}
salary_lm <- lm(salary ~ rank + discipline + yearsphd + yearsfac + sex, data = faculty)
summary(salary_lm)
#p-value for sex 0.21584
```

```{r exclude yearsfac and yearsphd and gender}
salary5_lm<-lm(salary ~ rank + discipline, data = faculty)
summary(salary5_lm)
AIC(salary5_lm)
```


```{r exclude yearsfac and yearsphd}
salary2_lm<-lm(salary ~ rank + discipline + sex, data = faculty)
summary(salary2_lm)
```
####This explains 44% (0.4407) of the variation seen in salary. 
###Years since receiving PhD and Years on faculty were found to be colinear, with a correlation coefficient of 0.9096491. 
###Yearsfac has a negative coefficient, indicating that as years spent as faculty increases, salary decreases. This is not logical, and was omitted from the final lm. 
###Rank appeared to be closely tied to Yearsphd and Yearsfac. When lm were run ony including rank, yearsphd, yearsfac, the adjusted R^2 were 0.4469, 0.2447, 0.1646 respectively. 
###lm was run for a version including both rank and yearsphd, and one for only including rank. Resulting adjusted R^2 was 0.4401, 0.4412 and the AIC was 9097.22, 9095.454 respectively. Seeing as adjusted R^2 was not improved with the additional variable, yearsphd was dropped from the final model. 
###Although the p-value for gender was not significant in the final model (p=0.245291), gender was included because gender accounts for a $4492 difference in salary. This fact is significant because this means that with all other variables constant, females will be paid $4492 less then men. 

```{r exclude yearsfac}
salary3_lm<-lm(salary ~ rank + discipline + yearsphd + sex, data = faculty)
summary(salary3_lm)
```

```{r exclude yearsphd}
salary4_lm<-lm(salary ~ rank + discipline + yearsfac + sex, data = faculty)
summary(salary4_lm)
#negative coefficient for yearsfac. Does not make sense 
```

```{r aic}
AIC(salary_lm) #9093.826, 0.4547, 0.4463
AIC(salary2_lm) #9095.454, 0.4469, 0.4412 <-choose this one 
AIC(salary3_lm) #9097.22, 0.4472, 0.4401
AIC(salary4_lm) #9096.813, 0.4478, 0.4407 
AIC(salary5_lm) #9094.823, 0.445, 0.4407 <- Possibly compare. Model excludes gender
```


```{r model_table, results = 'asis'}
stargazer(salary2_lm, type="html",
          title = "Iris regression results.")

```

###Exploring rank, yearsfac, yearsphd
```{r}
rank_lm<-lm(salary ~ rank + discipline  + sex, data = faculty)
summary(rank_lm)
```

```{r}
rank_lm2<-lm(salary ~ yearsfac + discipline  + sex, data = faculty)
summary(rank_lm2)
```

```{r}
rank_lm3<-lm(salary ~ yearsphd + discipline  + sex, data = faculty)
summary(rank_lm3)
```

#Data Exploration 

```{r salary in yearsphd comparing gender}
plt<-ggplot(faculty, aes(y=salary, x=yearsphd, group=sex))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE, aes(color=sex))
plt
```

```{r salary by rank and gender}
plt2<-ggplot(faculty, group=discipline)+
  geom_point(aes(x=discipline, y=salary, color=rank, shape=sex), position=position_dodge(width = .5))
plt2
```

#Exploring dependence 
```{r rank}
#Rank is not independent of gender. This is something to consider. 
t.rank<-table(faculty$sex, faculty$rank)
ct<-chisq.test(t.rank)
ct$expected
ct$observed
ct$stdres
ct ##p-value = 0.01408

```

```{r yearsphd and yearsfac cor}
##years fac vs. years phd
cor(faculty$yearsphd, faculty$yearsfac) 
#0.9096491
```


```{r salary by rank and yearsphd}
plt4<-ggplot(faculty, group=rank)+
  geom_point(aes(x=yearsphd, y=salary, color=rank), position=position_dodge(width = .5))
plt4
```

```{r salary by rank and yearsfac}
plt5<-ggplot(faculty, group=rank)+
  geom_point(aes(x=yearsfac, y=salary, color=rank), position=position_dodge(width = .5))
plt5
```