---
title: "Q3_Assignment5_206"
author: "Juan Silva"
date: "11/29/2018"
output: html_document
---

3) Male and female salaries for starting postdoctoral and other employment positions (2015). Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions: Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?

```{r setup, include=FALSE}

library(tidyverse)

mediansalary <- read_csv("mediansalary.csv")

# Wilcoxon Signed-Rank
# Null H: Ranks are equal
# Alt H: Ranks are NOT equal


wsr_salary <- wilcox.test(mediansalary$m_employment, mediansalary$f_employment, paired = TRUE)
wsr_salary

# There is a significant difference in median salaries between female and male in other employments (V = 101, p-value = 0.002572)

wsr_salarypostdoc <- wilcox.test(mediansalary$m_postdoc_study, mediansalary$f_postdoc_study, paired = TRUE)
wsr_salarypostdoc

# There is no significant difference in median salaries between female and male in post doc positions (V = 19.5, p-value = 0.8884)

```

```{r}
# Graphically show the differences in median salaries

graphmediansalary <- ggplot(mediansalary, aes(x = `Field of study`, y = m_employment)) +
  geom_bar()

graphmediansalary

# I don't know how to do this 
```


