---
title: "Q4_Assignment5_206"
author: "Juan Silva"
date: "11/29/2018"
output: html_document
---


4) Exploring academic salaries for professors in U.S. colleges. Explore relationships between variables in the ‘Faculty salary data (2008 - 2009 survey)’ dataset. Develop a model describing faculty salary based on data for faculty sex, rank, years in current position, field, and number of years since doctoral degree was earned. You should make decisions regarding which variables should remain in your final model. Describe the results qualitatively and quantitatively (i.e., don’t just report the statistical results of the model – make sure you describe interesting findings in text). You can also discuss any concerns that you have with the model(s) you present, if any.

```{r setup}


library(tidyverse)
library(stargazer)
library(MASS)

# sex, rank, years in current position, field, and number of years since doctoral degree was earned

faculty <- read_csv("Faculty.csv")
View(faculty)
faculty <- rename(faculty, discipline = `Discipline (A = Theoretical, B = Applied)`, rank = `Faculty Rank`, yearsphd = `Years Since PhD`, yearsfac = `Years Faculty Service`, sex = Sex, salary = `Salary ($)`)


# a. Saturated model: 

facultysalariesm <- lm(salary ~ rank + discipline + yearsphd + yearsfac + sex, data = faculty)

summary(facultysalariesm)

 # b. Alternative model without sex:

facultysalariesm2 <- lm(salary ~ rank + discipline + yearsphd + yearsfac, data = faculty)
summary(facultysalariesm2)

# ANOVA for model 1 and 2

anova(facultysalariesm, facultysalariesm2)

# AIC for models 1 and 2

aic1 <- AIC(facultysalariesm)
aic2 <- AIC(facultysalariesm2)
AIC(facultysalariesm, facultysalariesm2, exp3, exp6, exp7, exp8, exp9)

# c. Alternative model without

summary(facultysalariesm)$coefficient
```

```{r stargazer, results = 'asis'}

stargazer(facultysalariesm, type = "html")
```

#Further exploring 
```{r}
fit <- lm(salary ~ rank + discipline + yearsfac+rank:sex, data = faculty)
summary(fit)
fit2 <- lm(salary ~ rank + yearsfac+discipline:sex, data = faculty)
fit3 <- lm(salary ~ rank + discipline + yearsfac+yearsfac:sex, data = faculty)
summary(fit)
summary(fit2)
summary(fit3)
step <- stepAIC(fit, direction="both")
step$anova # display results



q<-ggplot(faculty,aes(x=sex, y=salary))+
  geom_point()+
  geom_boxplot()
q
```

```{r}
head(faculty)
cor(faculty$salary, faculty$yearsphd)
plot(faculty$yearsphd[faculty$sex=="Male"], faculty$salary[faculty$sex=="Male"], col = 'blue')
points(faculty$yearsphd[faculty$sex=="Female"], faculty$salary[faculty$sex=="Female"], col = 'red')
abline(a=101428.7, b=747.6, col = 'blue')
abline(a=92356.9, b=747.6, col = 'red')

exp <- lm(salary ~ yearsfac+sex, data = faculty)
summary(exp)
```
```{r}
remove.packages(MASS) 
library(dplyr)
faculty1<-faculty %>% 
  mutate(rank1=factor(faculty$rank))%>%
  mutate(sex1=factor(faculty$sex)) %>% 
  mutate(discipline1=factor(faculty$discipline)) %>% 
  dplyr::select(yearsphd:discipline1) %>% 
  dplyr::select(-sex)
 
names(faculty1)
exp2<-lm(salary~ yearsphd + yearsfac+ rank1 + sex1 + discipline1, data = faculty1)
summary(exp2)

```
```{r}
plt<-ggplot(faculty1, aes(y=salary, x=yearsphd, group=sex1))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE, aes(color=sex1))
plt
```



```{r}

plt2<-ggplot(faculty1, group=discipline1)+
  geom_point(aes(x=discipline1, y=salary, color=rank1, shape=sex1), position=position_dodge(width = .5))
plt2
##Appears like only men who are professors are paid higher in the ranks 
```

```{r}
exp3<-lm(salary~ discipline1+rank1 + yearsphd+sex1+sex1:yearsphd, data = faculty1)
summary(exp3)

exp6<-lm(salary~ discipline1+rank1 + sex1, data = faculty1)
summary(exp6)

exp7<-lm(salary~ discipline1+rank1, data = faculty1)
summary(exp7)

exp8<-lm(salary~ discipline1+sex1+yearsphd, data = faculty1)
summary(exp8)

exp9<-lm(salary~ discipline1+sex1, data = faculty1)
summary(exp9)
```

```{r}
t.test(faculty1$salary~faculty1$sex1)
```

```{r}
t.test(faculty1$salary~faculty1$discipline1)
```

```{r}
anova<-aov(salary ~ rank1, data = faculty1)
summary(anova)
TukeyHSD(anova)
plot(anova, 1)

one.anova<-oneway.test(salary ~ rank1, data = faculty1)
summary(one.anova)
```

#Are variables gender dependent 
```{r rank}
#Rank is not independent of gender. This is something to consider. 
t.rank<-table(faculty1$sex1, faculty1$rank1)
ct<-chisq.test(t.rank)
ct$expected
ct$observed
ct$stdres
ct ##p-value = 0.01408
```


```{r discipline}

##Independent of gender 
t.dis<-table(faculty1$sex1, faculty1$discipline1)
chisq.test(t.dis)
dt$expected
dt$observed
dt$stdres ##p=1
```

```{r}
##years fac vs. years phd
cor(faculty1$yearsphd, faculty1$yearsfac)
```

